Conservation decision-making under long transients

### 2019-08-09 slides/boettiger.Rmd
WIP

```{r arima_forecast}
arima_forecast %>% ggplot(aes(t)) + 
  geom_line(aes(y=x), col="white") +
  geom_line(aes(y=pred), col="grey", lwd = 1) + 
  geom_ribbon(aes(y=pred, ymin=pred-se, ymax=pred+se), fill="white", alpha = 0.5)

@@

@@

# A look at a candidate model

@@

```{r theory_f, fig.height=5.5}
p <- list(r = .05, K = 2, Q = 5, H = .38, sigma = .02, a=0.023, 
          N = 4e3, x0 = 0.2, N = 1e4)
theory(p) %>%
  ggplot(aes(x, y, col=curve)) +
  geom_line(lwd = 2)

@@

```{r posteriors, fig.width=12.5, fig.height=7}
label <- c("no switch", "switch", "no ghost")

@@

vp <- grid::viewport(width = 4, height = 0.8, x = 0.3, y = 0.7)

>>>>

```{r arima_data}
arima_forecast %>% filter(t < 2000) %>%
  ggplot(aes(t)) + 
  geom_line(aes(y=x), col="white") +
  geom_line(aes(y=pred), col="grey", lwd = 1) + 
  geom_ribbon(aes(y=pred, ymin=pred-se, ymax=pred+se), fill="white", alpha = 0.5) + 
  xlim(0,3000) + ylim(0, 1.6)+ ylab("x")

@@

```{r arima_forecast1}
arima_forecast %>% ggplot(aes(t)) + 
  geom_line(aes(y=pred), col="grey", lwd = 1) + 
  geom_ribbon(aes(y=pred, ymin=pred-se, ymax=pred+se), fill="white", alpha = 0.5) + 
  xlim(0,3000) + ylim(0, 1.6) + ylab("x")
```

```{r arima_forecast}
arima_forecast %>% ggplot(aes(t)) + 
  geom_line(aes(y=x), col="white") +
  geom_line(aes(y=pred), col="grey", lwd = 1) + 
  geom_ribbon(aes(y=pred, ymin=pred-se, ymax=pred+se), fill="white", alpha = 0.5)  + 
  xlim(0,3000) + ylim(0, 1.6)+ ylab("x")

# Statistical Issues

# Theoretical Issues

@@

### A look at a candidate model

@@

```{r theory_f, fig.height=5.2}
p <- list(r = .05, K = 2, Q = 5, H = .38, sigma = .02, a=0.023, 
          N = 4e3, x0 = 0.2, N = 1e4)
theory(p) %>%
  ggplot(aes(x, y, col=curve)) +
  geom_line(lwd = 2)

@@

```{r posteriors, fig.width=13, fig.height=6}
label <- c("no switch", "switch", "no ghost")

@@

vp <- grid::viewport(width = .5, height = 0.55, x = 0.35, y = 0.7)
